### 2016-10-25 paper/evaluation.tex
Updated evaluation

To evaluate the frequency of time-consuming regression tests, we first
compiled the project and test source files, later, we measured the
elapsed time to run the tests via the build system ignoring
non-related tasks (\eg, \emph{javadoc} generation).  We grouped the
resulting time from test executions into four different groups: tests
that ran in less than one minute (\emph{short execution}), one to five
minutes (\emph{normal execution}), five to ten minutes (\emph{long
execution}), and more than ten minutes to execute (\emph{very long
execution}).  Figure~\ref{fig:timecost-barplot} shows the distribution
of subjects per group. It is important to mention that
Figure~\ref{fig:timecost-barplot} represents a lower bound for elapsed
time: since the subjects were tested in a potentially unstable
revision, some tests may fail, interrupting the execution.

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.5\textwidth]{results/rq1/plots/piechart.pdf}
    \caption{\label{fig:timecost-barplot} Subjects grouped by elapsed
    time on test execution ($t$): short execution ($t < 1m$), normal
    execution ($1m \leq t < 5m$), long execution ($5m \leq t <
    10m$), and very long execution ($10m \leq t$).}
\end{figure}

@@

%% \begin{figure}[t!]
%%     \centering
%%     \includegraphics[width=0.5\textwidth]{plots/teststime-scatter/timetests-scatter.pdf}
%%     \caption{\label{fig:timetests-scatter} \Fix{...}}
%% \end{figure}

>>>>

\Fix{TODO: MERGE VERY LONG INTO LONG}
To evaluate the frequency of time-consuming regression tests, we first
compiled the project and test source files, later, we measured the
elapsed time to run the tests via the build system ignoring
non-related tasks (\eg, \emph{javadoc} generation).  We grouped the
resulting time from test executions into four different groups: tests
that ran in less than one minute (\emph{short execution}), one to five
minutes (\emph{normal execution}), five to ten minutes (\emph{long
execution}), and more than ten minutes to execute (\emph{very long
execution}).  Figure~\ref{fig:piechart-time} shows the distribution
of subjects per group. It is important to mention that
Figure~\ref{fig:piechart-time} represents a lower bound for elapsed
time: since the subjects were tested in a potentially unstable
revision, some tests may fail, interrupting the execution.

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.5\textwidth]{results/rq1/plots/piechart.pdf}
    \caption{\label{fig:piechart-time} Subjects grouped by elapsed
    time on test execution ($t$): short execution ($t < 1m$), normal
    execution ($1m \leq t < 5m$), long execution ($5m \leq t <
    10m$), and very long execution ($10m \leq t$).}
\end{figure}

@@

\begin{figure}[h!]%
    \centering
    \manpage{}
    \subfigure[\Fix{normal}]{
        \includegraphics[width=0.3\textwidth]{results/rq1/plots/scatterplot-norm.pdf}
    }
    \\
    \subfigure[\Fix{long}]{
        \includegraphics[width=0.3\textwidth]{results/rq1/plots/scatterplot-long.pdf}
    }\\
    \subfigure[\Fix{vlong}]{
        \includegraphics[width=0.3\textwidth]{results/rq1/plots/scatterplot-vlong.pdf}
    }
    \\
    \caption{\Fix{...}}
\end{figure}
